Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
more quotes

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- I don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Desirability}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown. Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

@@

\subsubsection{Visit Frequency}
% no significant effects on photo desirability $\chi^2(1,128) = 0.32$, p = 0.2858(> 0.05)
% most - 15%, least - 10%
%  no significant effects on video/trip desirability $\chi^2(1, 126) = 0.552$, p = 0.2288(> 0.05)
% most - 11%, least - 18%
We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind. Rewinds containing a location visited most frequently by the participant are kept 8\% of the time. This percentage increases significantly if the Rewind contains the location visited least frequently by the participant. Rewinds that include the least visited location are kept 13\% of the time. This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.

>>>>

\subsubsection{Travel Companions}
% trip accompanies have siginificant effects on both location and trip rememberance. 
% location rememberance: travel alone -  100%, not alone - 55%, $\chi^2(1,94) = 31.812$, p < 0.01
% trip rememberance: travel alone - 62%, not alone - 90%, $\chi^2(1,133) = 9.016$, p < 0.01
Our study shows that both location and trip remembrances are influenced by the presence of travel companions, yet in a opposite way. For location rememberance, participants who believed that they traveled alone reported 100\% successful recalls of locations compare to 55\% rate reported by participants who believed that they traveled in groups, with $\chi^2(1,94) = 31.812$, $p < 0.00001$. On the other hand, trip details tend to be more easily remembered during accompanied visits as one participant recalled ``I remembered my friend and i walked a certain way -- don't usually take this route". Participants who believed that they traveled alone were able to remember the exact trip 62\% of the time from watching Rewinds, yet those who believed that they traveled with companions could remember the exact trip 90\% of the time, with $\chi^2(1,133) = 9.016$, p = 0.0013 $(< 0.01)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Desirability}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. One participant expressed his interestes in Rewind, saying ``Would keep photos that I know/can place in context, but would keep every single video... cool to look back on where you were, what you did/as a record". Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown. Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

@@

\subsubsection{Visit Frequency}
% no significant effects on photo desirability $\chi^2(1,128) = 0.32$, p = 0.2858(> 0.05)
% most - 15%, least - 10%
%  no significant effects on video/trip desirability $\chi^2(1, 126) = 0.552$, p = 0.2288(> 0.05)
% most - 11%, least - 18%
We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind. Rewinds containing a location visited most frequently by the participant are kept 8\% of the time. Reactions from the participants were experience-dependent.
Some expressed that they ``Didn't need any more memories of work"; the others felt ``I used to work here, good memories, good vibes, good experience'', ``Nostalgic, reminds me of where i grew up". This percentage increases significantly if the Rewind contains the location visited least frequently by the participant. Rewinds that include the least visited location are kept 13\% of the time. This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.
